The National Eutrophication Survey: lake characteristics and historical nutrient concentrations

### 2017-12-04 08_manuscript/post_response.tex
typo fixes
fix figure legend colors

\begin{figure*}[t]
  \includegraphics[width=12cm]{points_regions-crop.pdf}
  \caption{Survey locations colored by sampling year (1972 northeastern-red, 1973 southeastern-green, 1974 central-blue, 1975 western-grey).}\label{fig:points_regions}
\end{figure*}

@@

The present study is the first to leverage digital transcription technologies to unlock the full NES dataset. In this paper, we describe the digital transcription of the full NES dataset with the goal of making the dataset openly accessible to the research community. Specifically, our objective was to exactly reproduce the contents of the original dataset rather than to evaluate the its integrity. We introduce and publish the data in an open format that requires no proprietary software. It can be easily downloaded, used for analysis, and amended. The provided summary statistics and figures also allow users to quickly assess the utility of the data. Finally, the code and raw data files are provided to facilitate the extraction of fields not represented in our completed dataset (mostly phytoplankton diversity data).

@@

% \begin{acknowledgements}
% TEXT
% \end{acknowledgements}

>>>>

\begin{figure*}[t]
  \includegraphics[width=12cm]{points_regions-crop.pdf}
  \caption{Survey locations colored by sampling year (1972 northeastern-light blue, 1973 southeastern-blue, 1974 central-light green, 1975 western-green).}\label{fig:points_regions}
\end{figure*}

@@

The present study is the first to leverage digital transcription technologies to unlock the full NES dataset. In this paper, we describe the digital transcription of the full NES dataset with the goal of making the dataset openly accessible to the research community. Specifically, our objective was to exactly reproduce the contents of the original dataset rather than to evaluate its scientific integrity. We introduce and publish the data in an open format that requires no proprietary software. It can be easily downloaded, used for analysis, and amended. The provided summary statistics and figures also allow users to quickly assess the utility of the data. Finally, the code and raw data files are provided to facilitate the extraction of fields not represented in our completed dataset (mostly phytoplankton diversity data).

@@

\begin{acknowledgements}

\end{acknowledgements}
